---
title: "PA1md.Rmd"
author: "SungChan Lee"
date: "2016/2/4"
output: html_document
---

## Code for reading in the dataset and/or processing the data
```{r, eval=FALSE, echo=TRUE}
library(ggplot2)

# read in data files
setwd("e:\\RExercise\\reproducible research")
activity <- read.csv("activity.csv")
```


## Histogram of the total number of steps taken each day
```{r, echo=TRUE}

library(ggplot2)

# read in data files
setwd("e:\\RExercise\\reproducible research")
activity <- read.csv("activity.csv")

# histogram without imputing
total_steps_per_day <- aggregate(steps~date, data=activity, FUN=sum, na.rm=TRUE)
View(total_steps_per_day)

hist(total_steps_per_day$steps, xlab="Total(steps) per day", main="Mean Total Number of Step per day <Before inputing>")
```

## Mean and median number of steps taken each day
```{r}
mean_steps_per_day <- setNames(aggregate(steps~date, activity,FUN =mean), c("Date", "Mean.steps.per.day"))
median_steps_per_day <- setNames(aggregate(steps~date, activity, FUN=median), c("Date", "Median.steps.per.day"))

#mean_steps_per_day
#median_steps_per_day
stat_per_day <- merge(mean_steps_per_day,median_steps_per_day)
stat_per_day$Date <- as.Date(stat_per_day$Date, format="%Y-%m-%d")
stat_per_day

```

## Time Series plot of the average number of steps taken
```{r, echo=TRUE}
ave_steps_per_interval <- aggregate(steps~interval, data=activity, FUN=mean, na.rm=TRUE, na.action=NULL)

qplot(interval, steps, data=ave_steps_per_interval, geom="line", xlab="Interval", ylab="Average number of steps taken")

```

## The 5-minute interval that, on average, contains the maximum number of steps
```{r, echo=TRUE}

v <- ave_steps_per_interval[ave_steps_per_interval$steps == max(ave_steps_per_interval$steps), ]
v
```

## Code to describe and show a strategy for imputing missing data

Strategy consists of following steps   
- calculate mean steps for each interval   
- this mean value will be used for missing values   
- replicate 61 times since there are 60 intervals in the data   
- to vectorize rbind rows into long vectors   
- calculate na vector for step column   
- imput NAs with average of the interval   

```{r, echo=TRUE}
# imputing

# calculate mean steps for each interval
# this mean value will be used for missing values
ave_steps_per_interval <- aggregate(steps~interval, data=activity, FUN=mean, na.rm=TRUE, na.action=NULL)

#replicate 61 times since there are 60 intervals in the data
#to vectorize rbind rows into long vectors
long_ave_steps_per_interval <- ave_steps_per_interval
for(i in 1:60) {
  long_ave_steps_per_interval <- rbind(long_ave_steps_per_interval, ave_steps_per_interval)
}

#calculate na vector for step column
na_vectors <- is.na(activity$steps)

#imput NAs with average of the interval
activity[na_vectors, ]$steps <- long_ave_steps_per_interval[na_vectors,]$steps
```

## Histogram of the total number of steps taken each day after missing values are imputed
```{r, echo=TRUE}

# show histogram after imputing
total_steps_per_day <- aggregate(steps~date, data=activity, FUN=sum)
View(total_steps_per_day)

hist(total_steps_per_day$steps, xlab="Total(steps) per day", main="Mean Total Number of Step per day <After imputing>")
```

## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r, echo=TRUE}
# calculate average steps for day

library(chron)
is_weekend <- is.weekend(activity$date)
activity$weekend <- "Weekday"
activity[is_weekend, ]$weekend <- "Weekend"

ave_steps_per_day <- aggregate(steps~interval+weekend, data=activity, FUN=mean)

qplot(interval, steps, data=ave_steps_per_day, geom="line", facets = .~weekend)

```